Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
draft of Code Availability and Data Citations

\noindent Data Citations, Code Availability, Data Availability

\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

\subsection*{Code availability}

\todo[inline]{provide supporting source code; explain how/where other may
access data underlying the analysis}

\todo[inline]{if using custom code for dataset generation/processing: indicate
how code can be accessed (including restrictions to access)}

\todo[inline]{include infos on versions of used software}

\todo[inline]{any specific variables or parameters used to generate, test, or process the current dataset?}

@@

\todo[inline]{clean the PPA dataset; upload as zip to zalando again?}

Bibliographic information for the data records described in the manuscript.

1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).

% cut anno
\citep{haeusler2016cutanno}
% speech anno
\citep{hausler2021studyforrest}
% audio-description
\citep{hanke2014audiomovie}
% movie
\citep{hanke2016simultaneous}
% localizer
\citep{sengupta2016extension}

>>>>

\noindent Data Citations, Code Availability
\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

\subsection*{Data and code availability}

Raw data, analysis scripts, and results: TBA. Zenodo (registered but zipped)
vs. OSF (datalad dataset but probably unregistered)

@@

% cut anno
1. Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
locations, and temporal progression in the motion picture "Forrest Gump".
\emph{F1000Research}
\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
(2016)

% speech anno
2. Häusler, C. O. \& Hanke M. \emph{OSF}
\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
(2020).

% audio-description
3. Hanke, M., Baumgartner, F. J., Ibe, P., Kaule, F. R., Pollmann, S., Speck,
O., Zinke, W. \& Stadler, J. \emph{OpenNEURO}
\href{https://openneuro.org/datasets/ds000113}{ds000113} (2014). \todo{4
datasets \& using authors/year of the audio-description}
